My title

### 2022-03-21 outputs/paper/paper.Rmd
Remove hash library and add figure captions

```{r crime-count-plot-by-education, fig.cap="Crime By Education Level", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
# university_crime_count
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)
```

@@

```{r sex_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
sex_crime_plot
```

```{r culture_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r race_skin_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical_appearance_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual_orientation_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical_mental_disability_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language_crime_plot, echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```

>>>>

```{r crime-count-plot-by-education, fig.cap="Crime By Education Level", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
university_crime_count
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)

# sex_crime_plot
```

@@

I plotted the relationships between all discrimination types and crime categories from Figure \@ref(fig:sex_crime_plot) to Figure \@ref(fig:language_crime_plot).

```{r sex-crime-plot, fig.cap="Sex Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
sex_crime_plot
```

```{r, culture-crime-plot, fig.cap="Ethnicity or culture Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r, race-skin-crime-plot, fig.cap="Race and Skin Color Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical-appearance-crime-plot, fig.cap="Physical appearance Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion-crime-plot, fig.cap="Religion Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual-orientation-crime-plot, fig.cap="Sexual orientation Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age-crime-plot, fig.cap="Age Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical-mental-disability-crime-plot, fig.cap="Physical or mental disability Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language-crime-plot, fig.cap="Language Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```
